manuscript - APP

### 2018-07-19 R/manuscript_app_alt_clean.Rmd
new code

theme_set(theme_bw(16))
source("tools.R")
```

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    here::here("..", "data", "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

# Exp 2b
df_exp2b <- 
  readRDS(
    here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
 filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_faster = (targetk > restk))
participants_exp2b <- 
  read.csv(here::here("..", "data", "exp2b", "participants_171023.csv"))
```

@@

```{r Charts1b}
accu_summary %>% 
  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
  geom_jitter() 
accu_summary %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, colour = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
```

@@

@@

### As factor
```{r}
# as factor and without contrast==0
ezANOVA(accu_summary_wo_0,
        accu, id, within = .(contrast_abs_f, target_straight))
```

@@

>>>>

theme_set(theme_bw(16))
source("tools.R")

data_pth <- here::here("..", "data")
```

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

# Exp 2b
df_exp2b <- 
  readRDS(
    file.path(data_pth, "exp2b", "responses", "responses_171023.rds")) %>% 
 filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_faster = (targetk > restk))
participants_exp2b <- 
  read.csv(file.path(data_pth, "exp2b", "participants_171023.csv"))
```

@@

@@

```{r Charts1b}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +

  theme(aspect.ratio = 1) + 
  xlab("c") + ylab("Accuracy")
```

```{r Charts1b without one participant}
accu_summary %>% 
  filter(id!= 13)
  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
  geom_jitter() 
accu_summary %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, colour = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
```

@@

### As factor
```{r}
# as factor and without contrast==0
ezANOVA(accu_summary_wo_0,
        accu, id, within = .(contrast_abs_f, target_straight),detailed = T)$ANOVA %>% 
  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
         partial_eta = (SSn/(SSn+SSd)) %>% round(2))

### Post hoc tests

```{r}
(accu_summary_wo_0 %>% 
  filter(contrast_abs_f == 1) %>% 
ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
         partial_eta = (SSn/(SSn+SSd)) %>% round(2))

(accu_summary_wo_0 %>% 
  filter(contrast_abs_f == 2) %>% 
ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
         partial_eta = (SSn/(SSn+SSd)) %>% round(2))

(accu_summary_wo_0 %>% 
  filter(contrast_abs_f == 3) %>% 
ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
         partial_eta = (SSn/(SSn+SSd)) %>% round(2))

(accu_summary_wo_0 %>% 
  filter(contrast_abs_f == 4) %>% 
ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
         partial_eta = (SSn/(SSn+SSd)) %>% round(2))

@@

```{r Charts2b without weird}
accu_summary %>% 
  filter(!id %in% weird_performance) %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_faster, colour = target_faster)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
```
